Staged Abstract Interpreter

### 2018-01-05 paper.tex
outline

Text of paper \ldots

>>>>

\textbf{Contribution(Proposed)}.

Show that abstract compilation can be understood as an instance of staged abstract interpreter.

We implement staged abstract interpreter in a big-step semantics (abstract definitional interpreter) 
using Scala with LMS framework. Show it generates sound and high-performance analysis code with 
various precisions and sensitivities, for examples, k-CFA, pushdown or m-CFA. 
Generate efficient store implementation.

Show the evaluation result on benchmark programs.

Can we do it with small-step semantics? or staging a transition system?

Modular analysis? For example, k-CFA (k > 0) is a naturally global program analysis, because 
it need the last k calling contexts. But can we analyze programs (libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

\section{Background}

\subsection{Abstracting Abstract Machine}

\subsection{Staged Interpreter}

\section{Abstract Compilation, Revisited}

\section{Staged Abstracting Abstract Machine}

\section{Evaluation}

\section{Related Work}

\textbf{Abstract Compilation}. The idea in this paper was closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be executed immediately in a higher-order language.

\citeauthor{Johnson:2013:OAA:2500365.2500604} in their work also adopt the 
idea closure generation for optimizing small-step abstracting abstract machine
\cite{Johnson:2013:OAA:2500365.2500604}.

\textbf{Abstracting Abstract Machine}. Abstracting Definitional Interpreter \cite{darais2017abstracting}

Collapsing Towers of Interpreters\cite{Amin:2017:CTI:3177123.3158140}

\section{Conclusion}
